---
title: "BetweenExpDifferences"
author: "Ben Peloquin"
date: "January 25, 2016"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 2
---

```{r}
rm(list = ls())
setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/analysis")
library(rjson)
library(jsonlite)
library(tidyr)
library(dplyr)
library(lme4)
library(lmerTest)
```


# Functionality
## read in literal listener data fn()
```{r}
# readLiteralListenerData()
# -------------------------
# filesPath :: path to directory with .json files ("../production-results/e8/")
readLiteralListenerData <- function(filesPath) {
  files <- dir(filesPath, pattern = "*.json")
  dRaw <- data.frame()  
  
  for (f in files) {
    jf <- paste(filesPath, f, sep="")
    jd <- fromJSON(paste(readLines(jf), collapse=""))
    id <- data.frame(workerid = jd$WorkerId,
                     scale = jd$answers$data$scale,
                     degree = jd$answers$data$degree,
                     stars = jd$answers$data$manipulation_level,
                     judgment = as.numeric(jd$answers$data$judgment),
                     language = jd$answers$data$language)
    dRaw <- bind_rows(dRaw, id)
  }
  dRaw
}
```

## read in Pragmatic listener data
```{r}
# readPragmaticListenerData()
# -------------------------
# filesPath :: path to directory with .json files ("../production-results/e8/")
readPragmaticListenerData <- function(filesPath) {
  files <- dir(filesPath, pattern = "*.json")
  dRaw <- data.frame()  
  
  if (grepl("e6", filesPath)) {
    for (f in files) {
      jf <- paste(filesPath, f, sep="")
      jd <- fromJSON(paste(readLines(jf), collapse=""))
      id <- data.frame(workerid = jd$WorkerId, 
                       scale = jd$answer$scale,
                       degree = jd$answer$degree,
                       stars = as.numeric(jd$answer$judgment),
                       language = jd$answer$language)
      dRaw <- bind_rows(dRaw, id)
    }
  } else if (grepl("e11", filesPath)) {
    for (f in files) {
    jf <- paste(filesPath, f, sep="")
    jd <- fromJSON(paste(readLines(jf), collapse=""))
    id <- data.frame(workerid = jd$WorkerId, 
                     scale = jd$answer$data$scale,
                     degree = jd$answer$data$degree,
                     stars = as.numeric(jd$answer$data$judgment),
                     language = jd$answer$data$language)
    dRaw <- bind_rows(dRaw, id)
    }
  } else stop("Must enter 'e6' or 'e11' for exp")
  
  dRaw
}
```

## get compliant worker ids
```{r}
# getCompliantWorkerIds()
# -----------------------
# df  :: data frame for exp
# exp :: experiment id 
getCompliantWorkerIds <- function(df, exp) {
  if (exp == "e8") {
    compliant <- df %>% 
      filter(tolower(language) == "english") %>%
      filter(grepl("training1", scale)) %>%
      group_by(workerid) %>%
      summarise(compliant = judgment[scale == "training1" & degree == "hi"] == 1 & 
                  judgment[scale == "training1" & degree == "low"] == 0)
  } else if (exp == "e10" | exp == "e12") {
    compliant <- df %>% 
      filter(tolower(language) == "english") %>%
      filter(grepl("training", scale)) %>%
      group_by(workerid) %>%
      summarise(compliant = (judgment[scale == "training1" & degree == "hi2"] == 1) && 
              (judgment[scale == "training1" & degree == "low1"] == 1))
  } else if (exp == "e6") {
    compliant <- df %>%
      filter(tolower(language) == "english") %>%
      filter(grepl("training1", scale)) %>%
      group_by(workerid) %>%
      summarise(compliant = stars[scale == "training1" & degree == "hi"] >= 4 &
                  stars[scale == "training1" & degree == "low"] <= 2)
  } else if (exp == "e11") {
    compliant <- df %>%
      filter(tolower(language) == "english") %>%
      filter(grepl("training1", scale)) %>%
      group_by(workerid) %>%
      summarise(compliant = stars[scale == "training1" & degree == "hi2"] >= 4 &
                  stars[scale == "training1" & degree == "low1"] <= 2)
  } else stop("Entered a bad experiment id (e6, e8, e10, e11, e12")
  # return compliant ids
  compliant
}
```

## get individual scalar items
```{r}
# lookupScalar()
# --------------
# degree :: scale degree ("hi", "low", "hi2" "h1", etc)
# scale  :: "some_all", "good_excellent"...
# exp    :: exp ide (e12, e8)
lookupScalar <- function(degree, scale, exp) {
  # some_all
  if (scale == "some_all") {
    if (exp == "e12") {
      if (degree == "hi1") return("all")
      if (degree == "hi2") return("most")
      if (degree == "mid") return("some")
      if (degree == "low1") return("little")
      if (degree == "low2") return("none")
    } else if (exp == "e10") {
      if (degree == "hi1") return("all")
      if (degree == "hi2") return("most")
      if (degree == "low1") return("some")
      if (degree == "low2") return("none")
    } else { ## must be exp 8
      if (degree == "hi") return("all")
      if (degree == "low") return("some")
    }
  # liked_loved
  } else if (scale == "liked_loved") {
    if (degree == "hi1" | degree == "hi") return("loved")
    if (degree == "hi2" | degree == "low") return("liked")
    if (degree == "mid") return("indifferent")
    if (degree == "low1") return("disliked")
    if (degree == "low2") return("hated")
  # good_excellent
  } else if (scale == "good_excellent") {
    if (degree == "hi1" | degree == "hi") return("excellent")
    if (degree == "hi2" | degree == "low") return("good")
    if (degree == "mid") return("okay")
    if (degree == "low1") return("bad")
    if (degree == "low2") return("horrible")
  # paltable_delicious
  } else if (scale == "palatable_delicious") {
    if (degree == "hi1" | degree == "hi") return("delicious")
    if (degree == "hi2" | degree == "low") return("palatable")
    if (degree == "mid") return("mediocre")
    if (degree == "low1") return("gross")
    if (degree == "low2") return("disgusting")
  # memorable_unforgettable
  } else if (scale == "memorable_unforgettable") {
    if (degree == "hi1" | degree == "hi") return("unforgettable")
    if (degree == "hi2" | degree == "low") return("memorable")
    if (degree == "mid") return("ordinary")
    if (degree == "low1") return("bland")
    if (degree == "low2") return("forgettable")
  }
  NA
}
```

# Literal Listener Data

## Get all L0 listener data
```{r echo = FALSE, message = FALSE, warning = FALSE}
e8 <- readLiteralListenerData("../production-results/e8/")
e10 <- readLiteralListenerData("../production-results/e10/")
e12 <- readLiteralListenerData("../production-results/e12/")
```

## Data org / cleaning / compliance checks
```{r}
# workerid as factor
e8$workerid <- as.factor(e8$workerid)
e8$exp <- "e8"
e10$workerid <- as.factor(e10$workerid)
e10$exp <- "e10"
e12$workerid <- as.factor(e12$workerid)
e12$exp <- "e12"

# Append compliance booleans
e8CompliantIds <- getCompliantWorkerIds(e8, "e8")
e8 <- left_join(e8, e8CompliantIds)
e10CompliantIds <- getCompliantWorkerIds(e10, "e10")
e10 <- left_join(e10, e10CompliantIds)
e12CompliantIds <- getCompliantWorkerIds(e12, "e12")
e12 <- left_join(e12, e12CompliantIds)
```

## Populate literal listener combined data
```{r}
# filter out compliance and training
allL0Listener <- rbind(e8, e10, e12) %>%
  subset(scale != "training1" & scale != "training2") %>%
  filter(compliant == TRUE)
## exp :: factor
allL0Listener$exp <- as.factor(allL0Listener$exp)
## judgment :: numeric
allL0Listener$judgment <- as.numeric(allL0Listener$judgment) 
allL0Listener$stars <- as.numeric(as.character(allL0Listener$stars)) / 20
str(allL0Listener)
```

### Add inidivual words
```{r}
allL0Listener$word <- as.factor(with(allL0Listener, mapply(lookupScalar, degree, scale, exp)))
```

## glmer()
```{r}
# fix contrasts so we're comparing most disparate experimetns (e8 and e12)
contrasts(allL0Listener$exp) <- cbind("e10" = c(1, 0, 0), "e8" = c(0, 0, 1))

# glmer WITHOUT experiment and with random effect for subjects
glm1 <- glmer(judgment ~ scale + stars + (1 | word) + (1 | workerid), data = allL0Listener)
# glmer WITH experiment and with random effect for subjects
glm2 <- glmer(judgment ~ exp + scale +  stars + (1 | word) +  (1 | workerid), data = allL0Listener)
```

## Visulaziations?
```{r}
# ggplot(allL0Listener, aes(x=stars, y=judgment, col=degree)) + 
#   geom_point(alpha = 0.5) +
#   geom_jitter(width = 0.1, height = 0.1) +
#   facet_wrap(~scale + exp)
```

## Model Comaprisons
```{r}
summary(glm2)
anova(glm1, glm2)
```
Looks like we dont' see a significant improvement in model fit when we include the fixed effect for experiment. Also, exp is not a significant predictor in the ME model.

# Pragmatic listener data

## Get all L1 listener data
```{r echo = FALSE, message = FALSE, warning = FALSE}
e6 <- readPragmaticListenerData("../production-results/e6/")
e11 <- readPragmaticListenerData("../production-results/e11/")
```

## Data org / cleaning / compliance checks
```{r}
# workerid as factor
e6$workerid <- as.factor(e6$workerid)
e6$exp <- "e6"
e11$workerid <- as.factor(e11$workerid)
e11$exp <- "e11"

# Append compliance booleans
e6CompliantIds <- getCompliantWorkerIds(e6, "e6")
e6 <- left_join(e6, e6CompliantIds)
e11CompliantIds <- getCompliantWorkerIds(e11, "e11")
e11 <- left_join(e11, e11CompliantIds)
```

## Populate pragmatic listener combined data
```{r}
# filter out compliance and training
allL1Listener <- rbind(e6, e11) %>%
  subset(scale != "training1" & scale != "training2") %>%
  filter(compliant == TRUE)
## exp :: factor
allL1Listener$exp <- as.factor(allL1Listener$exp)
str(allL1Listener)
```

### Add inidivual words
```{r}
allL1Listener$word <- as.factor(with(allL1Listener, mapply(lookupScalar, degree, scale, exp)))
```

## glmer()
```{r}
# glmer WITHOUT experiment and with random effect for subjects
glm1 <- lmer(stars ~ scale + (1 | word) + (1 | workerid), data = allL1Listener)
# glmer WITH experiment and with random effect for subjects
glm2 <- lmer(stars ~ exp + scale + (1 | word) +  (1 | workerid), data = allL1Listener)
```

## Model Comaprisons
```{r}
summary(glm2)
anova(glm1, glm2)
```
Looks like we dont' see a significant improvement in model fit when we include the fixed effect for experiment. Also, exp is not a significant predictor in the ME model.
