PSYCH 130 - EXPERIMENT 1 ANALYSIS
=================================

Preliminaries.

```{r}
rm(list=ls())
source("analysis/useful_dplyr.R")
library("rjson")
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("production-results/e1/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("production-results/e1/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   comparison = jd$answer$comparison,
                   scale = jd$answer$scale,
                   domain = jd$answer$domain,
                   rating = as.numeric(jd$answer$rating),
                   language = jd$answer$language)
  d.raw <- bind_rows(d.raw, id)
}
```

Exclude non-compliant participants and non-English speakers. 

```{r}
compliant <- d.raw %>% 
  filter(grepl("training", comparison)) %>%
  group_by(workerid) %>%
  summarise(compliant = rating[domain == "training2"] > 5)

d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", language, ignore.case = TRUE), 
         comparison != "training", 
         compliant == TRUE)
```

Note: we discovered that "upper" was miscoded in the experiment as "full" (they are flipped). Let's unflip them. 

```{r}
d$comparison <- factor(d$comparison, 
                       levels = c("upper", "lower", "full"), 
                       labels = c("full", "lower", "upper"))
```


Main Analysis
-------------

First look at means across scales. 

```{r}
ms <- d %>%
  group_by(scale, comparison) %>%
  summarise(n = n(),
            cil = ci.low(rating), 
            cih = ci.high(rating), 
            rating = mean(rating))

pdf("plots/e1.pdf")
qplot(x = scale, y = rating, 
      fill = comparison,
      geom = "bar", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = rating - cil, 
                     ymax = rating + cih),
                 position = position_dodge(width=.9))
dev.off()
```

Flip to make distance scores.

```{r}
dms <- d %>%
  group_by(scale, comparison) %>%
  mutate(dist = (6 - (rating - 1))/6) %>%
  summarise(n = n(),
            cil = ci.low(dist), 
            cih = ci.high(dist), 
            rating = mean(dist))

pdf("plots/e1_distance.pdf")
qplot(x = scale, y = rating, 
      fill = comparison,
      geom = "bar", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = rating - cil, 
                     ymax = rating + cih),
                 position = position_dodge(width=.9)) + 
  ylab("Distance (1 - similarity)")
dev.off()

pdf("plots/e1_upperonly.pdf")
qplot(x = scale, y = rating, 
      geom = "bar", stat = "identity", 
      position = "dodge", 
      data = filter(ms, comparison=="upper")) + 
  geom_linerange(aes(ymin = rating - cil, 
                     ymax = rating + cih),
                 position = position_dodge(width=.9)) + 
  ylim(c(0,1)) + 
  ylab("Distance (1 - similarity)")
dev.off()
```


Now break down by plurality. This isn't super interpretable. 

```{r}
msp <- d %>%
  mutate(plural = scale == "always_sometimes" |
           scale == "all_some" |
           scale == "three_two") %>%
  group_by(plural, comparison) %>%
  summarise(cil = ci.low(rating), 
            cih = ci.high(rating), 
            rating = mean(rating))

qplot(x = plural, y = rating, 
      fill = comparison,
      geom = "bar", stat = "identity", 
      position = "dodge", 
      data = msp) + 
  geom_linerange(aes(ymin = rating - cil, 
                     ymax = rating + cih),
                 position = position_dodge(width=.9))
```

Let's look at domains. 

```{r}
msd <- d %>%
  group_by(scale, domain, comparison) %>%
  summarise(n = n(), 
            cil = ci.low(rating), 
            cih = ci.high(rating), 
            rating = mean(rating))

qplot(x = scale, y = rating, 
      fill = comparison,
      geom = "bar", stat = "identity", 
      position = "dodge", 
      data = msd) + 
  facet_wrap( ~ domain) + 
  geom_linerange(aes(ymin = rating - cil, 
                     ymax = rating + cih),
                 position = position_dodge(width=.9))
```



