---
title: "The importance of negative alternatives in pragmatic implicature"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloquin@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract: 
    "Frameworks of pragmatic enrichment, starting with Grice 1975, implicitly assume the presence of salient alternatives. For example, the standard quantity implicature arises the presence of a competiting and more informative alternatives. Using a Bayesian formulzation of this theory we assess the degree to which alternatives influence pragmatic enrichment of scalar items. Our findings suggest that the presence of a complete of set of possible alternatives."
    
keywords:
    "pragmatics; scalar implicature; bayesian modeling"
    
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(ggplot2)
```

# Introduction

Implicature as a case study for pragmatics

RSA as a way of studying implicature [@frank2012]

Scalar implicature in particular, what are the alternatives? [@franke2014] [@degen2015]

Using the scalar diversity approach to get beyond the some/all implicature [@vantiel2013]
 
Outline of the rest of the paper

# Experiment 1a,b: Entailment scales

## Participants

## Procedure

## Results and Discussion



# Experiment 2: What are the alternatives?

## Participants

## Procedure

## Results and Discussion



# Experiment 3a,b: Adding Negative alternatives

## Participants

## Procedure

## Results and Discussion



# Model

## Details


## Model fitting and comparison



# General Discussion


# Acknowledgements

Thanks to NSF BCS #XYZ. Thanks to Michael Franke, Judith Degen, and Noah Goodman.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
