---
title: "Determining the alternatives for scalar implicature"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: 
    \author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloqui@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract: 
    Succesful communication regularly requires listeners to make pragmatic inferences - enrichments beyond the literal meaning of a speaker's utterance. For example, when interpreting a sentence such as "Bob ate some of the cookies," listeners routinely infer that Bob did not eat all of them. A Gricean account of this phenomena assumes the presence of alternatives (like "all of the cookies") with varying degrees of informativity, but it remains an open question precisely what these alternatives are. We use a computational model of pragmatic inference to test out hypotheses about how well different sets of alternatives allow us to predict scalar implicature performance across a range of different scales. Our findings suggest that human comprehenders likely consider a much broader set of alternatives beyond those entailed by the initial description.  
    
keywords:
    "pragmatics; scalar implicature; bayesian modeling"
    
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=TRUE, message=F, sanitize = T)
```

```{r, libraries}
library(ggplot2)
library(knitr)
library(rjson)
library(dplyr)
library(tidyr)
library(gridExtra)
library(jsonlite)
library(png)
library(grid)
library(xtable)
# library(langcog)
```


```{r helpers}
# lookupScalar()
# --------------
# degree :: scale degree ("hi", "low", "hi2" "h1", etc)
# scale  :: "some_all", "good_excellent"...
# exp    :: exp ide (e12, e8)
lookupScalar <- function(degree, scale, exp) {
  if (scale == "some_all") {
    if (exp == "e12") {
      if (degree == "hi1") return("all")
      if (degree == "hi2") return("most")
      if (degree == "mid") return("some")
      if (degree == "low1") return("little")
      if (degree == "low2") return("none")
    } else if (exp == "e10" | exp == "e11") {
      if (degree == "hi1") return("all")
      if (degree == "hi2") return("most")
      if (degree == "low1") return("some")
      if (degree == "low2") return("none")
    } else { ## must be exp 8
      if (degree == "hi") return("all")
      if (degree == "low") return("some")
    }
  # liked_loved
  } else if (scale == "liked_loved") {
    if (degree == "hi1" | degree == "hi") return("loved")
    if (degree == "hi2" | degree == "low") return("liked")
    if (degree == "mid") return("indifferent")
    if (degree == "low1") return("disliked")
    if (degree == "low2") return("hated")
  # good_excellent
  } else if (scale == "good_excellent") {
    if (degree == "hi1" | degree == "hi") return("excellent")
    if (degree == "hi2" | degree == "low") return("good")
    if (degree == "mid") return("okay")
    if (degree == "low1") return("bad")
    if (degree == "low2") return("horrible")
  # paltable_delicious
  } else if (scale == "palatable_delicious") {
    if (degree == "hi1" | degree == "hi") return("delicious")
    if (degree == "hi2" | degree == "low") return("palatable")
    if (degree == "mid") return("mediocre")
    if (degree == "low1") return("gross")
    if (degree == "low2") return("disgusting")
  # memorable_unforgettable
  } else if (scale == "memorable_unforgettable") {
    if (degree == "hi1" | degree == "hi") return("unforgettable")
    if (degree == "hi2" | degree == "low") return("memorable")
    if (degree == "mid") return("ordinary")
    if (degree == "low1") return("bland")
    if (degree == "low2") return("forgettable")
  }
  NA
}

normedVec <- function(vec) vec / sum(vec)
```

```{r, data}
# All scales studied
# ------------------
scales <- c("good_excellent",
            "liked_loved",
            "palatable_delicious",
            "memorable_unforgettable",
            "some_all")
# Experiment E9: Alternatives
# ---------------------------
alternativesData <- read.csv("../models/model_data/e9_alternativeCounts.csv",
                             stringsAsFactors = FALSE)
allModelRunData <- read.csv("../models/model_data/allModelRuns.csv",
                     stringsAsFactors = FALSE)

# Non-summarized data
# -------------------
allLiteralListener <- read.csv("../models/model_data/RawLiteralListenerCombined.csv", 
                               stringsAsFactors = FALSE)
allPragmaticListener <- read.csv("../models/model_data/RawPragmaticListenerCombined.csv", 
                               stringsAsFactors = FALSE)

# Model run data
# --------------
# Speakers ::
speakerE12 <- read.csv("../models/model_data/L0_e12.csv", stringsAsFactors = FALSE)
speakerE10 <- read.csv("../models/model_data/L0_e10.csv", stringsAsFactors = FALSE)
# speakerE8 <- read.csv("../models/model_data/L0_e8.csv", stringsAsFactors = FALSE)
speakerE8 <- read.csv("../models/model_data/L0_e8Compliance.csv", stringsAsFactors = FALSE)
# Listeners ::
listenerE6 <- read.csv("../models/model_data/L1_e6.csv", stringsAsFactors = FALSE)
listenerE11 <- read.csv("../models/model_data/L1_e11.csv", stringsAsFactors = FALSE)

# \begin{center}
# \textit{``When I choose a word," Humpty Dumpty said, in a rather scornful tone, ``it means just what I choose it to mean - neither more nor less"- Lewis Caroll, Through the Looking-Glass}
# \end{center}
```

# Introduction

How much of what we mean comes from the words that go unsaid? As listeners, the ability to enrich a speaker's meaning in context is an indispensable component of successful communication.  For example, listeners  commonly enrich the meaning of the scalar item *some* to *some but not all* in sentences like "Alice ate some of the cookies" [@grice1975;@horn1984;@levinson2000]. These inferences, called _scalar implicatures_, have been an important test case for understanding pragmatic inferences more generally. A Gricean account of this phenomena assumes listeners reason about the meaning the speaker intended by incorporating knowledge about a) alternative scalar items a speaker could have used (such as *all*) and b) the relative informativity of using such alternatives [@grice1975]. According to this account, a listener will infer that the speaker must have intended that Alice did not eat *all* the cookies because it would have been *underinformative* for the speaker to use *some* when *all* could have been used.

But how much of the meaning of *some* comes from the alternatives that weren't chosen? Put differently, what are the alternatives that should be considered in this computation more generally? Under classic accounts of implicature, listeners consider only those words whose meaning would entail the word that is actually sent [@horn1972], and these alternatives enter into conventionalized or semi-conventionalized scales [@levinson2000]. For example, because *all* entails *some*, and hence is a "stronger" meaning, *all* should be considered as an alternative to *some* in implicatures. Similar scales exist for non-quantifier scales, e.g. *loved* entails *liked* (and hence "I liked the movie" implicates that I didn't love it).

Recent empirical evidence has called into question whether entailment scales are all that is necessary for understanding scalar implicature. For example, @degen2015  demonstrated that the scalar item *some* was judged less appropriate when exact numbers were seen as viable alternatives. And in a different paradigm, @vantiel2014 found converging evidence that *some* was judged to be atypical for small quantities. These data provide indirect evidence about a broader set of alternatives: since *some* is logically true of sets with one or two members, these authors argued that the presence of salient alternatives (the words *one* and *two*) reduced the felicity of *some* via a pragmatic inference. 

By formalizing pragmatic reasoning, computational models can help provide more direct evidence about the role that alternatives play. The "rational speech act" model (RSA) is one recent framework for understanding inferences about meaning in context [@frank2012;@goodman2013]. RSA models frame language understanding as a special case of social cognition, in which listeners and speakers reason recursively about one another's goals. In the case of scalar implicature, a listener makes a probabilistic inference about what the speaker's most likely communicative goal was, given that she picked the quantifier *some* rather than the stronger quantifier *all*. In turn, the speaker reasons about what message would best convey her intended meaning to the listener, given that he is reasoning in this way. This recursion is grounded in a "literal" listener who reasons only according to the basic truth-functional semantics of the language. 

@franke2014 used an RSA-style model to assess what alternatives a speaker would need to consider in order to produce the typicality/felicity ratings reported by @degen2015 and @vantiel2014. In order to do this, @franke2014's model assigned weights to a set of alternative numerical expressions. Surprisingly, along with weighting *one* highly (a conclusion that was suppored by the empirical work), the best-fitting model assigned substantial weight to *none* as an alternative. This finding was especially surprising considering the emphasis of standard theories on scalar items that stand in entailment relationships with one another (e.g. *one* entails *some* even if it is not classically considered to be part of the scale).

In our current work, we pick up where these previous studies left off,  considering the set of alternatives for implicature using the RSA model. To gain empirical traction on this issue, however, we broaden the set of scales we consider. Our inspiration for this move comes from work by @vantiel2014b, who examined a phenomenon that they dubbed "scalar diversity," namely the substantial difference in the strength of scalar implicature across a variety of scalar pairs (e.g. *liked/loved,* or *palatable/delicious.*). Making use of some of this diversity allows us to investigate the ways that different alternative sets give rise to implicatures of different strengths across scales. 

We begin by presenting the computational framework we use throughout the paper. We next describe a series of experiments designed to measure both the literal semantics of a set of scalar items and comprehenders' pragmatic judgments for these same items. These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgements. To preview our results: we find that standard entailment alternatives do not allow us to fit participants' judgements, but that expanding the range of alternatives empirically (by asking participants to generate alternative messages) allows us to model listener judgements with high accuracy. 

# Modeling Implicature Using RSA

We begin by giving a brief presentation of the basic RSA model. This model simulates the judgements of a pragmatic listener who wants to infer a speaker's intended meaning $m$ from her utterance $u$. For simplicity, we present a version of this model in which there is only full recursion: that is, the pragmatic listener reasons about a pragmatic speaker, who in turn reasons about a "literal listener." We assume throughout that this computation takes place in a signaling game [@lewis1969] with a fixed set of possible meanings $m \in M$ and a fixed possible set of utterances $u \in U$, with both known to both participants. Our goal in this study is to determine what utterances fall in $U$.

In the standard RSA model, the pragmatic listener (denoted $L_1$), makes a Bayesian inference:

$$p_{L1}(m \mid u) \propto p_{S_1} (u \mid m) p(m)$$

\noindent In other words, the probability of a particular meaning given an utterance is proportional to the speaker's proability of using that particular utterance to express that meaning, weighted by a prior over meanings. This prior represents the listener's _a priori_ expectations about plausible meanings, independent of the utterance. Because our experiments take place in a context in which listeners should have very little expectation about which meanings speakers want to convey, for simplicity we assume a uniform prior $p(m) \propto 1$. 

The pragmatic speaker in turn considers the probability that a literal listener would interpret her utterance correctly:

$$ p_{S_1} (u \mid m) \propto p_{L_0} (m \mid u)$$

\noindent where $L_0$ refers to a listener who only considers the truth-functional semantics of the utterance (that is, which meanings the utterance can refer to). 

This model of the pragmatic speaker is consistent with a speaker who chooses words to maximize the utility of an utterance in context [@frank2012], where utility is operationalized as the informativity of a particular utterance (surprisal) minus a cost:

$$p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))},$$

\noindent where $C(u)$ is the cost of a particular utterance, $-log(p_{L_0})$ represents the _surprisal_ for the literal listener (the information content of the utterance), and ($\alpha$ is a parameter in a standard choice rule. If $\alpha=0$, speakers choose randomly and as $\alpha \rightarrow \infty$, they greedily choose the highest probability alternative. In our simulations below, we treat $\alpha$ as a free parameter and fit it to the data. 

To instantiate our signaling game with a tractable message set $M$, in our studies we adopt a food-review paradigm: we assume that speakers and listeners are trying to communicate the number of stars in an onine restaurant review (where $m \in \{1, 2, 3, 4, 5\}$). We then use experiments to measure three components of the model. First, to measure literal semantics ${p_{L_0} (m \mid u)}$ (we ask experiment participants to judge whether a message is applicable to a particular meaning (Experiment 1). Second, to generate a set of plausible alternative messages in $U$, we elicit alternatives directly (Experiment 2). Lastly, to obtain human $L_1$ pragmatic judgments, we ask participants to interpret a speaker's utterances (Experiment 3). 

# Experiment 1: Literal listener task

```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Stimuli for Experiments 1, 2, and 3"}

# Scale stimuli
grid::grid.raster(png::readPNG("figs/alternativeSets.png"))
```

```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 1 (literal listener) with the target scalar \`liked.\' (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \`liked.\'"}

# Screen shots of literal listener and pragmatic listener conditions
grid::grid.raster(png::readPNG("figs/exp1_stimuli.png"))
```

Experiment 1 was conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014. We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two alternatives ("entailment"), four alternatives, and five alternatives. The two-alternative entailment condition makes a test of the hypothesis that the two  members of the classic Horn scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference. The four- and five-alternative conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}

## Methods

### Participants

In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT). In the two-alternative condition, two participants were excluded because they reported having a native language other than English for a final sample of 28 participants. In the four-alternative condition,  six participants were excluded for either failing to pass two training trials a non-English native language, leaving a total sample of 24 participants. In the five-alternative condition, there were no data exclusions due to training failures or native language requirements, leaving a total sample of 30 participants.

### Design and procedure

Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup. Participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star rating. Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank. Each participant saw all scalar item and star rating combinations for their particular condition (see Figure \ref{fig:allScalesTable}), in a random oder.

The two-alternatives condition included only the scalar pairs from @vantiel2014. The four-alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 2. The five-alternatives condition included the four previous items plus one more "neutral" item chosen from those alternatives generated in Experiment 2. See Figure 1 for the complete list of alternatives used in each condition. 

## Results and Discussion

```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgements from Experiments 1a, 3a, and 4. Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).  Each panel shows one scalar pair."}

speakers <- bind_rows(speakerE12 %>% mutate(expt = "e12"), 
                      speakerE10 %>% mutate(expt = "e10"), 
                      speakerE8 %>% mutate(expt = "e8"))
speakers$scale <- as.factor(speakers$scale)

speakers$word <- as.factor(with(speakers, mapply(lookupScalar, degree, scale, expt)))
speakers$wordPlots <- factor(speakers$word, levels=c("excellent", "good", "okay", "bad", "horrible",
                           "loved", "liked", "indifferent", "disliked", "hated",
                           "unforgettable", "memorable", "ordinary", "bland", "forgettable",
                           "delicious", "palatable", "mediocre", "gross", "disgusting",
                           "all", "most", "some", "little", "none"))

# change col = word and facet_grid(.~scale)
ggplot(speakers, 
       aes(x = stars, y = speaker.p, col = scale, lty = expt)) + 
  geom_line() + 
  # facet_grid(.~ scale) + 
  facet_wrap(~wordPlots) +
  guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
                               title = "Scalar Item"), 
         linetype = guide_legend(direction = "horizontal", nrow = 1, 
                                 title = "Experiment")) + 
  xlab("star rating") +
  ylab("Proportion compatible") + 
  ggtitle("Scalar item literal semantic compatibility\nwith star ratings") +
  # scale_colour_solarized() + 
  theme_bw() +
  theme(strip.text.x = element_text(size = 8),
        legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 6))
```

Figure 2 plots literal listener $p_{L0}(m|u)$ distributions for the three conditions. Several trends are visible. First, in each scale, the alternatives spanned the star scale, such that there were alternatives that were highly compatible with both the lowest and highest numbers of stars. Second, there was clear variability between scalar families. For example, compatibility judgments for the top items in the *memorable / unforgettable* scale were more similar than those for *good / excellent* or *liked / loved.* Finally, there was substantial consistency in ratings for items that were repeated across experiments, suggesting that this paradigm elicited stable judgments from participants. 

# Experiment 2: Alternative Elicitation

To elicit empirical alternatives for the scales we used in Experiment 1, we adopted a modified cloze task inspired by Experiment 3 of @vantiel2014.

## Methods

### Participants

We recruited 30 workers on AMT. All participants were native English speakers and naive to the purpose of the experiment.

### Design and procedure

Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank. Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" They were prompted to generate three unique alternatives.

## Results and Discussion

```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements for our entailment scalar items. Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale. Each panel shows one scalar pair."}
# Get zero's in data frame
baseDf <- data.frame(degree = rep(c("hi", "low", "hi1", "hi2", "low1", "low2"), 25),
                     scale = c(rep("good_excellent", 6 * 5),
                               rep("liked_loved", 6 * 5),
                               rep("memorable_unforgettable", 6 * 5),
                               rep("palatable_delicious", 6 * 5),
                               rep("some_all", 6 * 5)),
                     stars = rep(1:5, 30),
                     combine = rep(TRUE, 150))
listeners <- bind_rows(listenerE6 %>% mutate(expt = "e6"), 
                      listenerE11 %>% mutate(expt = "e11"))
listeners <- left_join(baseDf, listeners) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p),
         expt = ifelse(degree == "hi" | degree == "low", "e6", "e11"))
listeners$word <- as.factor(with(listeners, mapply(lookupScalar, degree, scale, expt)))
listeners$plotThis <- with(listeners, ifelse(scale == "some_all" &
                               (degree == "hi" | degree == "low" | degree == "hi1" | degree == "low1"),
                               TRUE, ifelse(scale != "some_all" & (
                                 degree == "hi" | degree == "low" | degree == "hi1" | degree == "hi2"),
                                 TRUE, FALSE)))
listeners$scalarType <- with(listeners, ifelse(degree == "hi" | degree == "hi1", "stronger", "weaker"))
                               
# Plot pragmatic listener data here
ggplot(subset(listeners, plotThis == TRUE),
       aes(x = stars, y = listener.p, col = scalarType, lty = expt)) + 
  geom_line() + 
  facet_grid(.~ scale) + 
  ggtitle("Pragmatic listener judgments") +
  ylab("Proportion of stars selected") +
  xlab("Star rating") +
  theme_bw() +
  theme(strip.text.x = element_text(size = 6),
        legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8))
```

```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Caption goes here"}

# Subset alternatives for demo
plotData <- alternativesData %>%
  filter(scale == "liked_loved", alt != "liked", alt != "loved") %>%
  mutate(prop = n / sum(n))
  
# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
  geom_bar(stat="identity") + 
  ylim(0, 52) + 
  labs(x = "Alternatives", y = "Counts") +
  # theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
  theme_bw() +
  theme(strip.text.x = element_text(size = 8),
        legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5, size = 6),
        axis.text.y = element_text(size = 10))
```

Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar items *liked* and *loved* (combined). Alternative distributions for the other scalar pairs (e.g.. *good/excellent*, *memorable/unforgettable*) were similarly long-tailed.

# Experiment 3: Pragmatic Listener

Experiment 3 was conducted to measure pragmatic judgments $p_{L_1}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014. We include two conditions in Experiment 3. In the two-alternative entailment condition, participants made judgments for items included in the entailment scales. In the four-alternative condition, participants made pragmatic judgments for the entialment items and also the top two alternatives elicited for each scale in Experiment 2. Running two pragmatic judgment conditions allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions. \footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

## Participants

We recruited 100 participants from AMT, 50 for each condition. Data for 7 participants in the two-alternative condition were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of 43 participants. In the four-alternative condition, data from five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.

## Procedure

Participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave. Each participant was presented with all scalar items in a random order. The experimental setup is shown in Figure \ref{fig:expt1_stimuli}, right. 

## Results and Discussion



# Model Results

Using literal semantic data from Experiment 1 we conducted three simulations with our model. Each simulation used the specific literal semantic data to specify the scale representation available to our model. The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014). These data were measured in Experiment 1a. The "Top two" model extended the original set of alternatives with the top two alternatives generated in Experiment 2. These data were measured in Experiment 3a. The "Full" model included the full set of alternatives, including a neutral valenced alternative. These data were measured in Experiment 4.



```{r xtable, results = "asis", fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items. Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b. The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b."}
# Tuned model run data
plotData <- allModelRunData %>%
  mutate(study = ifelse(numAlts == 5, "Full", 
                        ifelse(numAlts == 4, "Top_two", "Entailment"))) %>%
  gather(Experiment, cors, c(corE6, corE11)) %>%
  mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))

tableCors <- plotData  %>%
  select(cors, study, Experiment) %>%
  unique() %>%
  mutate(Experiment = ifelse(Experiment == "1b", "Pragmatic_Listener_exp1", "Pragmatic_Listener_exp2")) %>%
  spread(Experiment, cors)
  
names(tableCors) <- c("r", "model", "Experiment")
tableCors <- tableCors[c(1, 3, 2),]
tab <- xtable(tableCors)
print(tab, type="latex")

# Correlation bar chart
corBarChart <- ggplot(plotData, aes(x=study, y=cors, fill = Experiment)) + 
  geom_bar(stat="identity", position="dodge") +
  ylab("Correlation") +
  xlab("Model") +
  ylim(0, 1) + 
  ggtitle("Model fit correlation coefficients") +
  guides(colour=FALSE) +
  geom_text(aes(x = study, y=as.numeric(cors) + 0.025, label = round(cors, 2), col=(Experiment)))

# Correlation scatter plot
symmetricCorPlot <- ggplot(subset(plotData, study == "Top_two"), aes(x = listener.p, y = preds)) + 
  geom_point() +
  xlab("Model predictions") +
  ylab("Human judgments") +
  stat_smooth(method = "lm") + 
  ggtitle("Model fit\nSymmetric scale")

# corBarChart

modifiedPlotData <- plotData %>%
  gather(pragStudy, pragChoice, c(9,11))
fullRepresentationFit <- qplot(stars, pragChoice, col=degree, shape = pragStudy,
      data=subset(modifiedPlotData, study == "Full")) +
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = preds), lty = 4)
# fullRepresentationFit
# gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))
```

# General Discussion

By varying the type of scale representations available to our Bayesian model we investigated the effects of alternatives on scalar implicature. Model fit with human judgement was significantly improved by the inclusion of alternatives beyond the typical "strong" and "weak" scalar items. In fact, we found that both neutral and negative valence scalar items contribute to human-like implicature generation within our framework. 


# Acknowledgements

Thanks to NSF BCS XYZ. Thanks to Michael Franke, Judith Degen, and Noah Goodman.

# References 

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
